### 2016-03-07 04-evaluation.tex
Use OpenMPI also for the qperf-style benchmark

Since the distributed algorithm is data-intensive, a key aspect in improving
its performance is to maximize the utility of the network resources.
In Figure~\ref{fig-qperf}, we provide maximum bandwidth numbers for
read operations between one server and one client for a range of payload sizes,
and compare these to the bandwidth achieved by an MPI roundtrip test,
and by \textit{qperf}~\cite{qperf-mellanox} which reports
the best achievable performance for Infiniband. We present \textit{qperf}
bandwidth for both RDMA read and RDMA write operations; these are quite
close, which corroborates the results from the Herd project for payloads
upwards from 256B.
The MVAPICH2 MPI implementation
is highly optimized for Infiniband. It requires an interaction between
the server network card and the server host, which increases the latency and
thus lowers the bandwidth
significantly. This is ample justification for using a low-level RDMA
implementation for the DKV store.
The bandwidth achieved by our DKV store falls short
of the \textit{qperf} performance for packets less than 4KB; this is attributed
to additional per-request overhead for the DKV store. For the largest packet
size, the DKV store performance is hampered by the fact that its values
are spread over a larger memory area, whereas \textit{qperf} and MPI always read
from the same memory locations. For packets between 8KB and 512KB, our DKV
achieves performance very close to \textit{qperf}.

>>>>

Since the distributed algorithm is data-intensive, a key aspect in improving
its performance is to maximize the utility of the network resources.
In Figure~\ref{fig-qperf}, we provide maximum bandwidth numbers for
read operations between one server and one client for a range of payload sizes,
and compare these to the bandwidth achieved by an MPI roundtrip test,
and by \textit{qperf}~\cite{qperf-mellanox} which reports
the best achievable performance for Infiniband. We present \textit{qperf}
bandwidth for both RDMA read and RDMA write operations; these are quite
close, which corroborates the results from the Herd project for payloads
upwards from 256B.
The OpenMPI implementation is highly optimized for Infiband because it has an
ib-verbs implmentation. It requires an interaction between
the server network card and the server host, which increases the latency and
thus lowers the bandwidth
significantly.
Note that the comparison is
lopsided: \textit{qperf} and MPI are low-level point-to-point benchmarks without
any DKV implementation on top.
This is ample justification for using a low-level RDMA
implementation for the DKV store.
The bandwidth achieved by our DKV store falls short
of the \textit{qperf} performance for packets less than 4KB; this is attributed
to additional per-request overhead for the DKV store. For the largest packet
size, the DKV store performance is hampered by the fact that its values
are spread over a larger memory area, whereas \textit{qperf} and MPI always read
from the same memory locations. For packets between 8KB and 512KB, our DKV
achieves performance very close to \textit{qperf}.
